Semi-supervised author disambiguation of scientific publications

### 2015-07-16 paper.tex
autosave

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by a same person. This
problem is often difficult because an author may use different spellings,
variants or synonyms across her career and/or distinct authors may share the
same name. Among solutions ot this problem, digital libraries are increasingly
offering tools for authors to manually curate their publications and claim
which ones are theirs. Indirectly, these tools allow for the inexpensive
collection of large annotated training data, which can be further leveraged to
build an automated disambiguation system capable of inferring features or
patterns for identifying publications written by a same person.  In this
context, we propose a semi-supervised machine learning disambiguation solution
in the case large and partially annotated databases of scientific publications.
Using a real-world dataset of 1 million manual annotations, we demonstrate how
we exploited this data (i) to learn an accurate classifier for identifying
corefering authors, (ii) to guide the clustering of scientific publications by
distinct authors in a semi-supervised way and finally (iii) to match the
resulting clusters with existing profiles.  Our analysis of parameters and
features on this large training set reveal that... \glnote{To be completed with
actual results.}

@@

Efforts and solutions to author disambiguation have been proposed from various
communities \citep{liu2014author}. On the one hand, libraries have maintained
authorship control through manual curation, either in a centralized way by
hiring collaborators or by developing services inviting authors to register
their publications themselves (e.g., Google Scholar, Inspire-HEP). Recently,
efforts started to assign persistent digital identifiers to researchers (e.g.,
ORCID, ResearchedID), with the further objective to embed these identifiers in
the submission workflow of publishers or repositeries (e.g., Elsevier, arXiv,
Inspire-HEP), thereby univocally solving any disambiguation issue. With the
large cost of centralized manual authorship control or until the larger
adoption of crowdsourced solutions, the impact of these efforts are
unfortunately limited by the efficiency, motivation and integrity of their
active contributors. For these reasons, fully automated machine learning-based
methods have been proposed during the past decade \glnote{Add references} to provide less costly and
more efficient solutions to author disambiguation. In this work, our goal is to
explore and demonstrate how both approaches can coexist and benefit from each
other.  In particular, we study how curated data obtained through manual
curation (either centralized or crowdsourced) can be exploited (i) to learn an
accurate classifier for identifying corefering authors, (ii) to guide the
clustering of scientific publications by distinct authors in a semi-supervised
way and finally (iii) to match the resulting clusters with existing profiles.
Our analysis of parameters and features on this large training set reveal
that... \glnote{To be completed with actual results.}

>>>>

Author name disambiguation in bibliographic databases is the problem of
grouping together scientific publications written by a same person, accounting
for potential homonyms and/or synonyms. Among solutions ot this problem, digital
libraries are increasingly offering tools for authors to manually curate their
publications and claim which ones are theirs. Indirectly, these tools allow for
the inexpensive collection of large annotated training data, which can be
further leveraged to build an automated disambiguation system capable of
inferring features or patterns for identifying publications written by a same
person.  In this context, we propose a semi-supervised machine learning
disambiguation solution in the case large and partially annotated databases of
scientific publications. Using a real-world dataset of 1 million manual
annotations, we demonstrate how we exploited this data (i) to learn an accurate
classifier for identifying corefering authors, (ii) to guide the clustering of
scientific publications by distinct authors in a semi-supervised way and
finally (iii) to match the resulting clusters with existing profiles.  Our
analysis of parameters and features on this large training set reveal that...
\glnote{To be completed with actual results.}

@@

Efforts and solutions to author disambiguation have been proposed from various
communities \citep{liu2014author}. On the one hand, libraries have maintained
authorship control through manual curation, either in a centralized way by
hiring collaborators or by developing services inviting authors to register
their publications themselves (e.g., Google Scholar, Inspire-HEP). Recently,
efforts also started to assign persistent digital identifiers to researchers
(e.g., ORCID, ResearchedID), with the further objective to embed these
identifiers in the submission workflow of publishers or repositeries (e.g.,
Elsevier, arXiv, Inspire-HEP), thereby univocally solving any disambiguation
issue. With the large cost of centralized manual authorship control or until
the larger adoption of crowdsourced solutions, the impact of these efforts are
unfortunately limited by the efficiency, motivation or integrity of their
active contributors. Similarly, the success of persistent digital identifier
efforts is conditioned to a large and ubiquituous adoption by both reseachers and publishers.
For these reasons, fully automated machine learning-based methods have been
proposed during the past decade \glnote{Add references} to provide immediate, less costly
and efficient solutions to author disambiguation. In this work, our goal
is to explore and demonstrate how both approaches can coexist and benefit from
each other.  In particular, we study how curated data obtained through manual
curation (either centralized or crowdsourced) can be exploited (i) to learn an
accurate classifier for identifying corefering authors, (ii) to guide the
clustering of scientific publications by distinct authors in a semi-supervised
way and finally (iii) to match the resulting clusters with existing profiles.
Our analysis of parameters and features on this large training set reveal
that... \glnote{To be completed with actual results.}
